Blocking-resistant communication through high-value web services

### 2014-05-13 docs/meek.tex
TLS handshake.

Two big things: list of ciphersuites and extensions.

% Examples of how handshakes differ; e.g., OpenSSL versus NSS,
% and non-browser NSS versus browser NSS.

@@

We implemented two versions of a browser extension, one for Firefox and one for Chrome.
They both work similarly: they open a TCP port on localhost,
await instructions from \meekclient\ on what HTTP requests to make,
issue the requests, and return the responses.

Figure~\ref{fig:browser-architecture} shows the interaction of components
on the user's computer.
Rather than starting \meekclient\ directly, the tor
process starts a helper process that starts both \meekclient\
and a headless browser instance.
The headless browser runs our extension in a separate
process and separate browser profile from the browser the
user interacts with; the two browser instances share no state.
\meekclient\ is configured to issue its requests through the browser extension;
in this configuration, the headless browser is the only thing that ever touches the network.

The use of a browser extension offers benefits beyond its TLS signature.
We inherit other characteristics of the browser:
how often it resolves DNS names,
its connection reuse,
and HTTP keepalive behavior.
The Firefox extension has special usability advantages because the Tor Browser Bundle
uses a modified Firefox.
We can include a small extension in the browser bundle and reuse the existing
Firefox executable without increasing the download size of the bundle much,
and without requiring users to separately configure a browser to run the extension.

>>>>

The practice of routing traffic through a web service with domain fronting
defeats both endpoint-based blocking and active scanning.
The endpoint (which appears to be the front domain; e.g. www.google.com)
cannot be blocked because to block it would cause collateral damage.
Active scanning is defeated because if the censor accesses the same
endpoint as the client, all they see is a web page served by the front domain.
Even though the censor knows some traffic is being fronted,
by looking only at IP addresses and domain names, it cannot determine which.

However, a savvy censor may also use content-based blocking
(deep packet inspection) as a basis for blocking.
Anything that reliably distinguishes meek's traffic from that of normal allowed traffic
(presumably web browsing) must be eliminated.
In this section we demonstrate how the client part of the TLS handshake can be used
to fingerprint different TLS implementations,
and how we use a web browser to camouflage meek's TLS.

There are many parts of the TLS handshake, but the two that
most distinguish the client are the list of ciphersuites and the
list of TLS extensions in the Client Hello.
Figure~\ref{fig:ciphersuites} shows how the list of ciphersuites
differs in different client implementations.
Figure~\ref{fig:ciphersuites:meek-client} is how our first prototype of \meekclient\ appeared on the wire,
using the built-in crypto/tls library of the Go programming language.
The list of ciphersuites is unlike that of a web browser,
and could be used as a fingerprint for blocking.
Tor itself was blocked by China in 2011 in exactly this way~\cite{bug4744}.
Similarly the list of TLS extensions (not shown)
differed between \meekclient\ and popular browsers.

\begin{figure}

\begin{subfigure}[t]{0.30\textwidth}
\begin{minipage}[t][17ex][t]{0.30\textwidth}
\tiny
\begin{verbatim}
TLS_ECDHE_RSA_WITH_AES_128_GCM_SHA256
TLS_ECDHE_ECDSA_WITH_AES_128_GCM_SHA256
TLS_ECDHE_RSA_WITH_RC4_128_SHA
TLS_ECDHE_ECDSA_WITH_RC4_128_SHA
TLS_ECDHE_RSA_WITH_AES_128_CBC_SHA
TLS_ECDHE_ECDSA_WITH_AES_128_CBC_SHA
TLS_ECDHE_RSA_WITH_AES_256_CBC_SHA
TLS_ECDHE_ECDSA_WITH_AES_256_CBC_SHA
TLS_RSA_WITH_RC4_128_SHA
TLS_RSA_WITH_AES_128_CBC_SHA
TLS_RSA_WITH_AES_256_CBC_SHA
TLS_ECDHE_RSA_WITH_3DES_EDE_CBC_SHA
TLS_RSA_WITH_3DES_EDE_CBC_SHA
\end{verbatim}
\end{minipage}
\caption{meek-client}
\label{fig:ciphersuites:meek-client}
\end{subfigure}
%
\begin{subfigure}[t]{0.30\textwidth}
\begin{minipage}[t][48ex][t]{0.30\textwidth}
\tiny
\begin{verbatim}
TLS_ECDHE_ECDSA_WITH_AES_256_CBC_SHA
TLS_ECDHE_ECDSA_WITH_AES_128_CBC_SHA
TLS_ECDHE_RSA_WITH_AES_128_CBC_SHA
TLS_ECDHE_RSA_WITH_AES_256_CBC_SHA
TLS_ECDHE_ECDSA_WITH_3DES_EDE_CBC_SHA
TLS_ECDHE_RSA_WITH_3DES_EDE_CBC_SHA
TLS_ECDHE_ECDSA_WITH_RC4_128_SHA
TLS_ECDHE_RSA_WITH_RC4_128_SHA
TLS_DHE_RSA_WITH_AES_128_CBC_SHA
TLS_DHE_DSS_WITH_AES_128_CBC_SHA
TLS_DHE_RSA_WITH_CAMELLIA_128_CBC_SHA
TLS_DHE_DSS_WITH_CAMELLIA_128_CBC_SHA
TLS_DHE_RSA_WITH_AES_256_CBC_SHA
TLS_DHE_DSS_WITH_AES_256_CBC_SHA
TLS_DHE_RSA_WITH_CAMELLIA_256_CBC_SHA
TLS_DHE_DSS_WITH_CAMELLIA_256_CBC_SHA
TLS_DHE_RSA_WITH_3DES_EDE_CBC_SHA
TLS_DHE_DSS_WITH_3DES_EDE_CBC_SHA
TLS_ECDH_ECDSA_WITH_AES_128_CBC_SHA
TLS_ECDH_RSA_WITH_AES_128_CBC_SHA
TLS_ECDH_ECDSA_WITH_AES_256_CBC_SHA
TLS_ECDH_RSA_WITH_AES_256_CBC_SHA
TLS_ECDH_ECDSA_WITH_3DES_EDE_CBC_SHA
TLS_ECDH_RSA_WITH_3DES_EDE_CBC_SHA
TLS_ECDH_ECDSA_WITH_RC4_128_SHA
TLS_ECDH_RSA_WITH_RC4_128_SHA
TLS_RSA_WITH_AES_128_CBC_SHA
TLS_RSA_WITH_CAMELLIA_128_CBC_SHA
TLS_RSA_WITH_AES_256_CBC_SHA
TLS_RSA_WITH_CAMELLIA_256_CBC_SHA
TLS_RSA_WITH_SEED_CBC_SHA
SSL_RSA_FIPS_WITH_3DES_EDE_CBC_SHA
TLS_RSA_WITH_3DES_EDE_CBC_SHA
TLS_RSA_WITH_RC4_128_SHA
TLS_RSA_WITH_RC4_128_MD5
\end{verbatim}
\end{minipage}
\caption{Firefox 24}
\label{fig:ciphersuites:firefox}
\end{subfigure}
%
\begin{subfigure}[t]{0.30\textwidth}
\begin{minipage}[t][27ex][t]{0.30\textwidth}
\tiny
\begin{verbatim}
TLS_ECDHE_ECDSA_WITH_AES_128_GCM_SHA256
TLS_ECDHE_RSA_WITH_AES_128_GCM_SHA256
TLS_DHE_RSA_WITH_AES_128_GCM_SHA256
TLS_ECDHE_ECDSA_WITH_CHACHA20_POLY1305_SHA256
TLS_ECDHE_RSA_WITH_CHACHA20_POLY1305_SHA256
TLS_RSA_WITH_AES_128_GCM_SHA256
TLS_ECDHE_ECDSA_WITH_AES_256_CBC_SHA
TLS_ECDHE_RSA_WITH_AES_256_CBC_SHA
TLS_DHE_RSA_WITH_AES_256_CBC_SHA
TLS_RSA_WITH_AES_256_CBC_SHA
TLS_ECDHE_ECDSA_WITH_RC4_128_SHA
TLS_ECDHE_ECDSA_WITH_AES_128_CBC_SHA
TLS_ECDHE_RSA_WITH_RC4_128_SHA
TLS_ECDHE_RSA_WITH_AES_128_CBC_SHA
TLS_DHE_RSA_WITH_AES_128_CBC_SHA
TLS_DHE_DSS_WITH_AES_128_CBC_SHA
TLS_RSA_WITH_RC4_128_SHA
TLS_RSA_WITH_RC4_128_MD5
TLS_RSA_WITH_AES_128_CBC_SHA
TLS_RSA_WITH_3DES_EDE_CBC_SHA
\end{verbatim}
\end{minipage}
\caption{Chrome 33}
\label{fig:ciphersuites:chrome}
\end{subfigure}

\caption{Differences in ciphersuites offered by
our \meekclient\ program when it accesses the network directly,
and by two web browsers.
The distinctive ciphersuites offered by \meekclient\ can be used as part of a blocking fingerprint.
As a remedy we have \meekclient\ proxy its TLS through a web browser extension.
}
\label{fig:ciphersuites}
\end{figure}

In response to the threat of TLS fingerprinting,
we modified \meekclient\ to proxy its HTTP requests through a local web browser extension.
\meekclient\ tells the extension what URLs to fetch, and the extension fetches them.
The TLS fingerprint looks like that of a browser, because it is that of a browser.
We implemented two versions of the extension, one for Firefox and one for Chrome.
They work similarly: they open a TCP port on localhost,
await instructions from \meekclient\ on what HTTP requests to make,
issue the requests, and return the responses.

@@

Figure~\ref{fig:browser-architecture} shows the interaction of components
on the user's computer.
Rather than starting \meekclient\ as a pluggable transport directly, the tor
process starts a helper process that starts both \meekclient\
and a headless browser instance.
The headless browser runs our extension in a separate
process and separate browser profile from the browser the
user interacts with; the two browser instances share no state.
\meekclient\ is configured to issue its requests through the browser extension;
in this configuration, the headless browser is the only thing that ever touches the network.
When run with a browser extension, meek has the same TLS signature
as Firefox (Figure~\ref{fig:ciphersuites:firefox}) or
Chrome (Figure~\ref{fig:ciphersuites:chrome}).

The use of a browser extension offers benefits beyond its TLS signature.
We inherit other characteristics of the browser:
how often it resolves DNS names,
its connection reuse,
and HTTP keepalive behavior.
The Firefox extension has special usability advantages because the Tor Browser Bundle
uses a modified Firefox.
We can include a small extension in the browser bundle, reusing the existing
Firefox executable, without increasing the download size of the bundle much,
and without requiring users to separately configure a browser to run the extension.

The development of the browser extensions posed some unexpected challenges.
Tor Browser disables TLS session tickets because they can be used as linking identifiers,
but the lack of session tickets shows up as a missing TLS extension,
so we had to reenable them in the headless browser.
(Doing so doesn't harm Tor Browser's anonymity:
if session tickets are used, they are used only on the circumvention layer
between the user and the frontend server. Tor Browser's own TLS is tunneled
within the circumvention layer, and session tickets are still disabled at that level.)
The Chrome extension needed to be split into two pieces, an extension and an app,
because an extension cannot open a listening socket and an app cannot make HTTP requests.
